descriptive_Clusters

### 2020-07-14 descriptive_Clusters.Rmd

#summarise by LADs per cluster and Total tests / Mean speed per cluster
LAD.cluster.tests <- clusters %>%
  group_by(cluster.tests) %>%
  summarise(n.LADs = n())
LAD.cluster.tests$Total <- TS2020 %>%
  group_by(cluster.tests) %>%
  summarise(n.cluster = n())
LAD.cluster.up <- clusters %>%
  group_by(cluster.up) %>%
  summarise(up.LADs = n())
LAD.cluster.up$Mean <- summarise(group_by(TS2020, cluster.up),
  mean(speedup))
LAD.cluster.up$SD <- summarise(group_by(TS2020, cluster.up),
  sd(speedup))
LAD.cluster.down <- clusters %>%
  group_by(cluster.down) %>%
  summarise(down.LADs = n())
LAD.cluster.down$Mean <- summarise(group_by(TS2020, cluster.down),
  mean(speeddown))
LAD.cluster.down$SD <- summarise(group_by(TS2020, cluster.down),
  sd(speeddown))
LAD.cluster.diffUp <- clusters %>%
  group_by(cluster.up.diff) %>%
  summarise(diffUp.LADs = n())
LAD.cluster.diffDown <- clusters %>%
  group_by(cluster.down.diff) %>%
  summarise(diffDown.LADs = n())

>>>>

#summarise by LADs per cluster and Total tests / Mean speed per cluster
LAD.cluster.tests <- clusters %>%
  group_by(cluster.tests) %>%
  summarise(n.LADs = n())
LAD.cluster.testsTotal <- TS2020 %>%
  group_by(cluster.tests) %>%
  summarise(n.cluster = n())
LAD.cluster.tests <- left_join(LAD.cluster.tests, LAD.cluster.testsTotal)
LAD.cluster.up <- clusters %>%
  group_by(cluster.up) %>%
  summarise(up.LADs = n())
LAD.cluster.upMean <- summarise(group_by(TS2020, cluster.up),
  mean(speedup))
LAD.cluster.upSD <- summarise(group_by(TS2020, cluster.up),
  sd(speedup))
LAD.cluster.up <- cbind(LAD.cluster.up, LAD.cluster.upMean[,2], LAD.cluster.upSD[,2])
LAD.cluster.down <- clusters %>%
  group_by(cluster.down) %>%
  summarise(down.LADs = n())
LAD.cluster.downMean <- summarise(group_by(TS2020, cluster.down),
  mean(speeddown))
LAD.cluster.downSD <- summarise(group_by(TS2020, cluster.down),
  sd(speeddown))
LAD.cluster.down <- cbind(LAD.cluster.down, LAD.cluster.downMean[,2], LAD.cluster.downSD[,2])
LAD.cluster.diffUp <- clusters %>%
  group_by(cluster.up.diff) %>%
  summarise(diffUp.LADs = n())
LAD.cluster.diffDown <- clusters %>%
  group_by(cluster.down.diff) %>%
  summarise(diffDown.LADs = n())

#write csvs to outputs
out.clustersLAD <- paste(path, "./data/temp/LAD.cluster.tests.csv", sep = "")
write_csv(LAD.cluster.tests, out.clustersLAD)
out.clustersLADup <- paste(path, "./data/temp/LAD.cluster.up.csv", sep = "")
write_csv(LAD.cluster.up, out.clustersLADup)
out.clustersLADdown <- paste(path, "./data/temp/LAD.cluster.down.csv", sep = "")
write_csv(LAD.cluster.down, out.clustersLADdown)
